\section*{Introduction}
I believe that there is great value in considering the human experience as the process of learning in an ever changing world. Learning, it seems, is fundamental to the human condition. And yet we find ourselves hard pressed to fully explain learning. I find it incredible that the process through which we come to understand the world can at once seem so intimate and so mysterious. 

Of course humanity is not the sole possessor of learning faculties. Contemporary society is filled with learning algorithms that shape our lives in ways we do not fully understand. Recommender systems promote information and products given our continual interactions with these algorithms. Google now incorporates machine learning into their search algorithms, though their implementations remain a closely guarded secret. These algorithms often utilize information gathered from large numbers of people, and they have the potential to steer practical consequences for countless individuals. These individuals often have little control over the algorithms they interact with, and the algorithms offer little in way of transparency. We find ourselves progressively moving into a world that is shaped by our interactions with learning algorithms.

My primary academic interest lies in the application of algorithms for sequential decision making under uncertainty. I believe that research in this area has the potential to augment human decision making in domains where either intuition fails us or where we are faced with combinatorial possibilities. I also believe that there is much work to be done where machine learning intersects with human computer interaction. It is my hope that the future design of machine learning algorithms will both empower the people interacting with them, and respect those individuals' autonomy. 